Testing d3

### 2024-06-20 text/22/r-creatures.Rmd
Update 2022 files, part 5

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
output: html_document
---

>>>>

---
title: "Different creatures in the R zoo"
author: "Steve Simon"
source: new
date: "2022-04-14"
category: 
- Blog post
tags:
- R software
output: html_document
page_update: complete
---

### 2024-06-20 text/22/testing-d3.Rmd
Reformatted tags in yaml headers
Update 2022 files, part 5

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: new
categories: 
- Blog post
tags: 
- Graphical display
output: html_document
---

>>>>

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: new
categories:
- Blog post
tags:
- Graphical display
output: html_document
page_update: complete
---
